Working with daily climate model output data in R and the \pkg{futureheatwaves} package

### 2016-12-31 paper_drafts/RJournalRevisions/anderson-eason-barnes.tex
Update paper draft

The following code gives an example of using a CMIP5 file and some of
the R packages and functions discussed. Results include a map of
near-surface air temperatures from a single climate model on a specific
day in July 2075 (Figure \ref{fig:worldmap}) and a time series of daily
near-surface air temperature simulations for the climate model grid
point closest to Beijing, China (Figure \ref{fig:timeseries}). To try
this example, you will need to download the file
``tas\_day\_GFDL-ESM2G\_rcp85\_r1i1p1\_20710101-20751231.nc'' from
\url{https://pcmdi.llnl.gov/search/cmip5/} and save it in the ``tmp''
subdirectory of your home directory.

>>>>

The functions and packages just described can be used to work with CMIP5
netCDF files in R to do things like map near-surface air temperatures
from a single climate model on a specific day in July 2075 (Figure
\ref{fig:worldmap}) and pull a time series of daily near-surface air
temperature simulations for the climate model grid point closest to
Beijing, China (Figure \ref{fig:timeseries}). The
``starting\_from\_netcdf'' vignette that comes with the
``futureheatwaves'' package provides all code required to create these
figures, as well as more details and code examples on working with CMIP5
netCDF files in R.
